Thesis Title

### 2022-05-16 chapters/introduction.tex
working version

Direct detection methods negate the need for virus propagation, detecting the virus directly from the suspect source through nucleic acid and immunological methods. 
\ac{PCR} and \ac{RT-PCR} are widely applied methods for the detection of both DNA and RNA viruses, respectively, driven by increased awareness of the clinical value of and demand for prompt information about viral loads, viral sequence data and potential antiviral resistance information \citep{cassedy_virus_2021}. 
Syndromic testing (see \secref{sssec:_intro_bacterial}) is now fully integrated into standard testing practises of many clinical laboratories \citep{dien_bard_panels_2020}. 
The limitations of these assays include the absence of detection of off-target pathogens, a lack of full susceptibility information, cost, and false positive results. 
\ac{qPCR} remains the front line tool in aetiological diagnosis, measuring the production of the target amplicon throughout the reaction and providing quantitative results with high specificity and sensibility, albeit with a significant cost due to sophisticated apparatus despite high-throughput systems being widely established \citep{cassedy_virus_2021}.

>>>>

Direct detection methods negate the need for virus propagation, detecting the virus directly from the suspect source through nucleic acid and immunological methods. 
\ac{PCR} and \ac{RT-PCR} are widely applied methods for the detection of both \ac{DNA} and \ac{RNA} viruses, respectively, driven by increased awareness of the clinical value of and demand for prompt information about viral loads, viral sequence data and potential antiviral resistance information \citep{cassedy_virus_2021}. 
Syndromic testing (see \secref{sssec:_intro_bacterial}) is now fully integrated into standard testing practises of many clinical laboratories \citep{dien_bard_panels_2020}. 
The limitations of these assays include the absence of detection of off-target pathogens, a lack of full susceptibility information, cost, and false positive results. 
\ac{qPCR} remains the front line tool in aetiological diagnosis, measuring the production of the target amplicon throughout the reaction and providing quantitative results with high specificity and sensibility, albeit with a significant cost due to sophisticated apparatus despite high-throughput systems being widely established \citep{cassedy_virus_2021}.
